\LARGE \bf Informed sampling by Markov Chain Monte Carlo methods

### 2017-02-09 paper.tex
add problem definition and start mcmc sampling

One of the popular classes of Monte Carlo simulation is 
\emph{Markov Chain Monte Carlo} (MCMC)~\cite{ADDJ03}.
Here, the samples are drawn by generating a Markov chain such that the distribution of points on the chain converges to the desired distribution.
The Markov Chain can be generated by performing a random walk such as
in Metropolis-Hastings~\cite{ADDJ03} or Gibbs sampling~\cite{ADDJ03}.
Alternatively, samples on the chain can be generated by simulating Hamiltonian dynamics~\cite{N11} (instead of performing the random walk).
This approach, termed Hybrid or Hamiltonian Monte Carlo (HMC)~\cite{N11} was shown to converge faster to the desired distribution, when compared to random-walk based MCMC algorithms.

@@

@@

Let $T(x_1, x_2)$ denote the minimal time to move the robot from state $x_1$ to $x_2$.
Furthermore, set
%
\begin{equation}
T(x) = T(x_s, x) + T(x, x_g).
\end{equation}
%
Namely, $T(x)$ is the minimal time to reach the goal from the start subject to passing through the state $x$.

\subsection{Informed set}
Recall that for Euclidean spaces minimizing path length, the informed set is a prolate hyperspheroid.
Moreover, this ellipsoid is defined only be the cost $\hat{c}$ of the current best solution and not by the location of the start and goal.

@@

See Fig. ~\ref{fig:sample_dimt} for an example motion of one joint through the $\left(x,\dot{x}\right)$ space.

@@

\dy{add a math description}

Define the dynamics of a robot as 
\begin{equation}
\label{eq:kinematics}
\dot{\bm{x}}(t) = f( \bm{x}(t) , \bm{u}(t) ), 
\end{equation}
in which $ \bm{x} \in \mathcal{X} \subseteq \mathbb{R}^n $ is the state of the robot, and $ \bm{u} \in \mathcal{U} \subseteq \mathbb{R}^m $ is the control input.
The dynamics determines a state trajectory $ \pi $, given a duration $ T $, an initial state $ \bm{x}(0) $ and an initial input $ \bm{u}(0) $.
The cost of a trajectory $ \pi $ is defined as the accumulated cost along the path, which is 
\begin{equation}
\label{eq:path_cost}
c(\pi) = \int_0^{T} c( x(t), u(t) ) dt.
\end{equation}
Consider the obstacles in a workspace, we have $ \mathcal{X}_{free} \subseteq \mathcal{X} $.
Consider the bounds of the control input, we have $ \mathcal{U}_{free} \subseteq \mathcal{U} $.
The dynamics of the robot in Equation~\eqref{eq:kinematics}, free state space $  \mathcal{X}_{free} $ and free control input space $ \mathcal{U}_{free} $ determines a free trajectory space $ \Pi_{free} $, which contains all feasible trajectories $ \pi \in \Pi_{free} $.

We can define an optimal kinodynamic path-planning problem that finds a kinodynamic path minimizing the cost in Definition \ref{defn:optimal_kino_path_planning}.
\begin{defn}{ \textbf{Optimal Kinodynamic Path-Planning} }
\label{defn:optimal_kino_path_planning}
	Find an optimal path $  \pi^* $ that satisfies
	\begin{itemize}
	\item $\forall t \in [0,T] $, $ \bm{x} (t) \in \mathcal{X}_{free}  $ and $ \bm{u} (t) \in \mathcal{U}_{free} $;
	\item $ \bm{x} (0) = x_{init} $, $ \bm{x} (T) = x_{goal} $, $ \bm{u} (0) = u_{init} $ and $ \bm{u} (T) = u_{goal} $; and
	\item $ \pi^* = \max_{ \pi \in \Pi_{free} } c( \pi ) $. 
	\end{itemize}
\end{defn}

\dy{Do we want to set an initial and a goal for the control input? Does this simplify the problem solving?}

@@

>>>>

One of the popular classes of Monte Carlo simulation is 
\emph{Markov Chain Monte Carlo} (MCMC)~\cite{ADDJ03}.
Here, the samples are drawn by generating a Markov chain such that the distribution of points on the chain converges to the desired distribution.
The Markov Chain can be generated by performing a random walk such as
in Metropolis-Hastings~\cite{CG95} or Gibbs sampling~\cite{CK94}.
Alternatively, samples on the chain can be generated by simulating Hamiltonian dynamics~\cite{N92} (instead of performing the random walk).
This approach, termed Hybrid or Hamiltonian Monte Carlo (HMC)~\cite{N11} was shown to converge faster to the desired distribution, when compared to random-walk based MCMC algorithms.

@@

Define the dynamics of a robot as 
\begin{equation}
\label{eq:kinematics}
\dot{\bm{x}}(t) = f( \bm{x}(t) , \bm{u}(t) ), 
\end{equation}
in which $ \bm{x} \in \mathcal{X} \subseteq \mathbb{R}^n $ is the state of the robot, and $ \bm{u} \in \mathcal{U} \subseteq \mathbb{R}^m $ is the control input.
The dynamics determines a state trajectory $ \pi $, given a duration $ T $, an initial state $ \bm{x}(0) $ and an initial input $ \bm{u}(0) $.
The cost of a trajectory $ \pi $ is defined as the accumulated cost along the path, which is 
\begin{equation}
\label{eq:path_cost}
c(\pi) = \int_0^{T} c( x(t), u(t) ) dt.
\end{equation}
Consider the obstacles in a workspace, we have $ \mathcal{X}_{free} \subseteq \mathcal{X} $.
Consider the bounds of the control input, we have $ \mathcal{U}_{free} \subseteq \mathcal{U} $.
The dynamics of the robot in Equation~\eqref{eq:kinematics}, free state space $  \mathcal{X}_{free} $ and free control input space $ \mathcal{U}_{free} $ determines a free trajectory space $ \Pi_{free} $, which contains all feasible trajectories $ \pi \in \Pi_{free} $.
An optimal kinodynamic path-planning problem that finds a kinodynamic path minimizing the cost $ \pi^* = \max_{ \pi \in \Pi_{free} } c( \pi ) $ subject to constraints $ \bm{x} (t) \in \mathcal{X}_{free}  $ and $ \bm{u} (t) \in \mathcal{U}_{free} $.

Informed sampling-based planning algorithms (e.g. Informed RRT*~\cite{GSB14}, BIT*~\cite{GSB15}) samples new states only from an \emph{informed set}.
An informed set is a subspace $ X_f \subseteq \mathcal{X}_{free} $  that is possible to provide better solution than the current best $  X_f = \{ x \in \mathcal{X}_{free} \mid c ( \pi^*(x) ) < c_{best} \} $~\cite{GSB14}, in which $ \pi^*(x) $ means the optimal path from $ x_{init} $ to $ x_{goal} $ constrained to pass through $ x $ and $ c_{best} $ is the cost of the current best found.
The current best $ c_{best} $ constrains eligible $ x $ indirectly by an implicit $ \pi^*(x) $.
In an optimal kinodynamic path-planning problem, more constraints are considered in defining an informed set, which include the system dynamic constraint and the boundary of control input.
If we consider a manifold that is defined by an informed set $ X_f $, the informed sampling becomes how to sample on this manifold in a high-dimensional space.

@@

Let $T(x_1, x_2)$ denote the minimal time to move the robot from state $x_1$ to $x_2$.
Furthermore, set
%
\begin{equation}
T(x_s, x, x_g) = T(x_s, x) + T(x, x_g).
\end{equation}
%
Namely, $T(x_s, x, x_g)$ is the minimal time to reach the goal from the start subject to passing through the state $x$.

\subsection{Informed set}
Recall that for Euclidean spaces minimizing path length, the informed set is a prolate hyperspheroid.
Moreover, this hyperspheroid is defined only be the cost $\hat{c}$ of the current best solution and not by the location of the start and goal.

@@

See Fig. ~\ref{fig:sample_dimt} for an example motion of one joint through the $\left(q,\dot{q}\right)$ space.

@@

\section{MCMC-based Informed Sampling}

@@

Rejection sampling is the simplest ways of constrained sampling~\cite{}, but is also known for high rejection-rate on a manifold in a high-dimensional space.
Hierarchical Rejection Sampling (HRS) is thus proposed .... 
However, the rejection rate is still relatively high~\cite{}.
In this paper, we propose an informed sampling by an MCMC approach.
In order to obtained uniformly sampling on a manifold, MCMC provides an approach that samples from a high-dimensional uniform distribution subject to a manifold constraint.
